### 2022-02-16 misc/solutions/prob-method-sols.tex
Exercise 3.1

\proclaim Exercise 1.7. Let $F$ be a finite collection of binary strings of finite lengths and assume no
member of $F$ is a prefix of another one. Let $N_i$ denote the number of strings of length $i$ in $F$.
Prove that
$$\sum_{i\ge 1} {N_i\over 2_i} \le 1.$$

@@

>>>>

\proclaim Exercise 1.8. Let $F$ be a finite collection of binary strings of finite lengths and assume no
member of $F$ is a prefix of another one. Let $N_i$ denote the number of strings of length $i$ in $F$.
Prove that
$$\sum_{i\ge 1} {N_i\over 2_i} \le 1.$$

@@

\goodbreak
\section 3. Alterations

\proclaim Exercise 3.1. As shown in Section~3.1, the Ramsey number $R(k,k)$ satisfies
$$R(k,k) > n-{n\choose k}2^{1-{k\choose 2}}$$
for every integer $n$. Conclude that
$$R(k,k) \ge \bigl(1-o(1)\bigr) {k\over e} 2^{k/2}.$$

\proof We set $n= (k-1) 2^{k/2} /e$ in the above, to get the bound
$$R(k,k) > {k\over e} 2^{k/2} - {1\over e} 2^{k/2} - {(k-1) 2^{k/2} /e \choose k} 2^{1-{k\choose 2}}.$$
Now we apply the inequality ${n\choose k} \le e^kn^k/k^k$, which yields
$$\eqalign{
R(k,k) &> {k\over e} 2^{k/2} - {1\over e} 2^{k/2} - {e^k(k-1)^k 2^{k^2/2} /e^k \over k^k} 2^{1-k^2/2+k/2}\cr
&= {k\over e} 2^{k/2} - {1\over e} 2^{k/2} - \biggl(1-{1\over k}\biggr)^k 2^{1+k/2}. \cr
}$$
Since $(1-1/k)^k\to 1/e$ as $k\to\infty$,
$$R(k,k) > {k\over e}2^{k/2} \biggl( 1 - {1\over k} - {2e(1-1/k)^k \over k}\biggr)
= {k\over e}2^{k/2} \bigl(1-o(1)\bigr).\noskipslug$$
